---
title: "packyak"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{packyak}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

[stephen@localhost rpmbuild]$ git config --global user.name "sagrudd"
[stephen@localhost rpmbuild]$ git config --global user.email "stephen@mnemosyne.co.uk"

xurl <- "https://bioconductor.org/packages/release/bioc/html/ShortRead.html"
xcontent <- httr::GET(xurl)
xtables <- rvest::html_nodes(httr::content(xcontent, encoding="UTF-8"), "table")




```{r setup}
library(packyak)
```

# starting with a basic server version of fedora 33
sudo yum install R

# enable password free sudo access

sudo visudo
<username>     ALL=(ALL) NOPASSWD:ALL


sudo yum install rpm-build git rpm-devel rpmlint rpmdevtools
sudo yum install libpng-devel bzip2-libs xz-devel libjpeg-devel openssl-devel icu



install.packages(c("cli", "stringr", "R6", "httr", "rvest", "lubridate", "git2r"))


packyak::PackYak$new(c("cli", "stringr", "R6", "httr", "rvest", "lubridate", "git2r", "knitr", "testthat", "rmarkdown"), build_rpm=TRUE)


packyak::PackYak$new(c("dplyr", "rlang", "purrr", "lubridate", "R6", "ggplot2", "RColorBrewer", "reshape2", "readr", "tidyr", "emojifont", "magrittr", "tibble", "aws.s3", "Rcpp", "Rsamtools", "cli", "stringr", "ShortRead"), build_rpm=TRUE)


